RadLib: a radiative heat transfer model library for CFD

### 2020-12-31 manuscript/manuscript.tex
minor edits to abstract, conclusions, and keywords

\begin{abstract}
%% Text of abstract 
Ca. 100 words
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
radiative heat transfer \sep reacting flows  \sep CFD
\end{keyword}

@@

Set out the conclusion of this original software publication.

>>>>

\begin{abstract}
RadLib is a modular C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interface options permit convenient expansion to additional models. Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. The computational cost of the models is also compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
radiative heat transfer \sep reacting flows  \sep CFD \sep WSGG \sep RCSLW
\end{keyword}

@@

RadLib is a C++ library of radiation property models developed to address the complexity and difficulty inherent in implementing radiative property models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit convenient expansion to additional property models. To that end, the basic structure and use of the RadLib library has been laid out. In addition, the RadLib package includes example cases in several variations of a parallel planes geometry using a simple ray tracing solver to illustrate the use of the three radiation property models. These examples are compared to line-by-line solutions. In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy, but, under the appropriate conditions, the PM and WSGG models can also perform well and boast lower computational costs than the RCSLW model. As a whole, RadLib provides a convenient access point for researchers that require radiation property models for simulation tools and can be applied to research problems in a variety of fields.
